Convex Surrogates via Polyhedral Losses

### 2019-04-30 neurips-19/cvx-fin.tex
update outline

\begin{itemize}
\item Def: order-sensitive, orderable.
\item Theorem (Lambert et al): $\ell$ order-sensitive iff $\prop{\ell}$ orderable.
\item Theorem: $\ell$ 1-embeddable iff $\ell$ 1-embeddable via polyhedral loss iff $\ell$ order-sensitive.
% \item Prop: Every polyhedral $L:\reals\to\reals^\Y$ embeds an order-sensitive $\ell$.
\item Prop: If convex $L:\reals\to\reals^\Y$ indirectly elicits finite $\gamma$, then $\gamma$ is orderable.
\item Theorem: TFAE for all the complexity classes.
\end{itemize}

@@

\begin{definition}\label{def:trim}
  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t. } \forall u'\in\R,u'\neq u,\, \Gamma_u \not\subseteq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
\end{definition}
\jessiet{What if $\Gamma_u = \Gamma_{u'}$?  Would we remove both copies of the level set as is?}
\raft{Note for later: should be able to show that the union of trim is the simplex.}

@@

\begin{theorem}\label{thm:polyhedral-embed}
  Every polyhedral loss embeds a finite elicitable property.
  Moreover, a polyhedral loss $L$ indirectly elicits \raft{NO LONGER DEFINED} a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
\end{theorem}

>>>>

\begin{itemize}
\item Def: order-sensitive, orderable.
\item Theorem (Lambert et al): $\ell$ order-sensitive iff $\prop{\ell}$ orderable.
\item Theorem: $\ell$ 1-embeddable iff $\ell$ order-sensitive.  Moreover,   1-embeddable implies 1-embeddable via polyhedral loss.
  % \item Prop: Every polyhedral $L:\reals\to\reals^\Y$ embeds an order-sensitive $\ell$.

\item Def: indirectly elicits (necessary but not sufficient for consistency).
\item Prop: If convex $L:\reals\to\reals^\Y$ indirectly elicits finite $\gamma$, then $\gamma$ is orderable.
\item Remark: TFAE for all the complexity classes (but don't define them rigorously).
\item Remark: Also, note that we have ``indirectly elicitable $\implies$ exists separated link'', so elicitation complexity does capture consistency here.
\item Cor: Abstain, mode, not embeddable / indirectly elicitable in 1d when $n\geq 3$.
\end{itemize}

@@

\begin{definition}\label{def:trim}
  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
\end{definition}
\jessiet{What if $\Gamma_u = \Gamma_{u'}$?  Wouldn't we remove both copies of the level set as is?}
\raft{Great point.  I changed to $\subsetneq$.}
\raft{Note for later: should be able to show that the union of trim is the simplex.}

@@

\begin{theorem}\label{thm:polyhedral-embed}
  Every polyhedral loss embeds a finite elicitable property.

  \raf{I think we should save this result for the next paper; it's more about complexity, and only needed for the corresponding 1d result, which we can probably prove more directly.} 
  Moreover, a polyhedral loss $L$ indirectly elicits a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
\end{theorem}
